---
title: "CPAL-CPAL260-sv"
output: html_document
date: "2026-02-04"
---

# setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## load libraries

```{r load_libraries, warning=FALSE, message=FALSE}

packages_needed <- c("readxl", "dplyr", "tidyverse",
                     "ggplot2", "ggspatial", "ggpubr", 
                     "reshape2", "runner", "grid")
# packages_needed <- c("RColorBrewer", ,
#                      "scales", "ggmap",
#                      "pophelper",
#                      "gridExtra", "label.switching", "remotes",
#                      "stringr", "writexl", "ggpmisc",
#                      "dismo", "maps", "mapdata",
#                      "adegenet", "poppr", "hierfstat",
#                      "vcfR", "ape", "pegas")

for(i in 1:length(packages_needed)){
  if(!(packages_needed[i] %in% installed.packages())){install.packages(packages_needed[i])}
  library(packages_needed[i], character.only = TRUE)
}

```

## define functions
### format FST DF
```{r define_prepFSTdf_FX}

FST_df_prep <- function(CHROMS_DF, POPLIST, FOCALPOP, WINDOW_SIZE, AVG_THRESH_CT, SUBSET_FACTOR) {
  
  #identify files to combine
  #COMPARISONS <- subset(POPLIST, !(POPLIST %in% FOCALPOP))
  WILDCARD1 <- paste0(BASEDIR, "fst/", FOCALPOP, "-*_subset", SUBSET_FACTOR, ".fst.txt")
  FILENAMES1 <- Sys.glob(WILDCARD1) 
  WILDCARD2 <- paste0(BASEDIR, "fst/*-", FOCALPOP, "_subset", SUBSET_FACTOR, ".fst.txt")
  FILENAMES2 <- Sys.glob(WILDCARD2)
  file_list <- c(as.list(FILENAMES1), as.list(FILENAMES2))
  FILENAMES <- c(FILENAMES1, FILENAMES2)

  #read in files
  fst_df <- file_list %>%
    set_names(nm = FILENAMES) %>%
    map_dfr(
      ~ read_delim(.x,
                   skip = 1,
                   col_types = cols(),
                   col_names = c("region", "chr", "midpos", "nsites", "fst"),
                   delim = "\t"),
      
      .id = "comparison"
    )
  
  colnames(CHROMS_DF) <- c("chr", "chr_num")
  fst_df <- fst_df %>%
    filter(chr %in% CHROMS_DF$chr)
  fst_df <- left_join(fst_df, CHROMS_DF, by = "chr")

  fst_df <- fst_df %>%
    mutate(tmp1 = gsub(paste0(BASEDIR, "fst/"), "", comparison)) %>%
    mutate(tmp1 = gsub(paste0("_subset", SUBSET_FACTOR, ".fst.txt"), "", tmp1)) %>%
    mutate(tmp2 = gsub(FOCALPOP, "", tmp1)) %>%
    mutate(POP2 = gsub("-", "", tmp2))
  fst_df$POP2 <- factor(fst_df$POP2, levels = POPLIST)
  fst_df$chr_num <- factor(fst_df$chr_num, levels = CHROMS_DF$chr_num)
  fst_df$fst_neg0 <- fst_df$fst
  fst_df$fst_neg0[fst_df$fst_neg0 < 0] <- 0
  
  fst_df <- fst_df %>% 
    arrange(POP2,chr,midpos)

  #sliding window
  window_df <- fst_df %>%
    mutate(window = (floor(midpos/WINDOW_SIZE) * WINDOW_SIZE) + (WINDOW_SIZE/2)) %>%
    group_by(POP2,chr,window) %>%
    summarize(window_fst = mean(fst_neg0), count=n(), POP2 = first(POP2), chr_num = first(chr_num)) %>%
    filter(count >= AVG_THRESH_CT)
  
  final_fst_df <- full_join(fst_df[c("chr","chr_num","midpos","fst_neg0","POP2")],
                             as.data.frame(window_df),
                             by = c("chr" = "chr", 
                                    "midpos" = "window", 
                                    "POP2" = "POP2", 
                                    "chr_num" = "chr_num"))

  final_fst_df

}

```

### plot pca
```{r plot_pca_fx}

plot_pca <- function(FEATURE_DF, COV_MATRIX) {
  pca_e <- eigen(COV_MATRIX)
  first3pcs <- data.frame(pca_e$vectors[,1:3])
  labeled_first3pcs <- cbind(FEATURE_DF,
                             pc1 = first3pcs$X1,
                             pc2 = first3pcs$X2,
                             pc3 = first3pcs$X3)
  pca_graph <- ggplot(labeled_first3pcs, aes(x = pc1, y = pc2, color = color_feature, fill = color_feature, shape = shape_feature)) + 
    geom_point(size = 3) +
    scale_fill_manual(values=opt1_region_palette) +
    scale_color_manual(values=opt1_region_palette) +
    scale_shape_manual(values=c("spawning" = 17, 
                                "non-spawning" = 19, 
                                "A" = 24, 
                                "B" = 21, 
                                "C" = 25,
                                "D" = 22,
                                "n/a" = 4)) +
    xlab(paste0("PC1 - ", sprintf("%0.2f", pca_e$values[1]), "%")) +
    ylab(paste0("PC2 - ", sprintf("%0.2f", pca_e$values[2]), "%"))
}

```

### beagle to heatmap df
```{r beagle2heatmapdf_fx}
beagle2heatmapdf <- function(beagle_filename){
  beagle_table <- read.table(beagle_filename)
  geno_matrix <- matrix(ncol = ((ncol(beagle_table)-3)/3), nrow = (nrow(beagle_table)-1))
  colnames(geno_matrix) <- paste0("Ind",1:((ncol(beagle_table)-3)/3))
  for(i in 2:nrow(beagle_table)){
    for(j in 6:ncol(beagle_table)){
      if(j%%3 == 0){
        hom_major <- as.double(beagle_table[i,(j-2)])
        het <- as.double(beagle_table[i,(j-1)])
        hom_minor <- as.double(beagle_table[i,(j)])
        probs <- c(hom_major, het, hom_minor)
        
        if(probs[1] == probs[2] & probs[1] == probs[3]){
          geno_matrix[(i-1),((j/3)-1)] <- NA
        } else if(probs[1] == max(probs) & probs[1] == probs[2]){
          geno_matrix[(i-1),((j/3)-1)] <- 1 + probs[1]
        } else if(probs[1] == max(probs) & probs[1] == probs[3]){
          geno_matrix[(i-1),((j/3)-1)] <- "NO"
        } else if(probs[2] == max(probs) & probs[2] == probs[3]){
          geno_matrix[(i-1),((j/3)-1)] <- 3 + probs[2]
        } else if(max(probs) == probs[1]){
          geno_matrix[(i-1),((j/3)-1)] <- abs(probs[1]-1)
        } else if(max(probs) == probs[2]){
          geno_matrix[(i-1),((j/3)-1)] <- 2 + probs[2]
        } else if(max(probs) == probs[3]){
          geno_matrix[(i-1),((j/3)-1)] <- 4 + probs[3]
        }
      }
    } 
  }
    
  ## convert matrix to datatable for plotting
  geno_table <- reshape2::melt(geno_matrix)
    
  ## Rename columns 
  colnames(geno_table) <- c("locus", "Ind", "value")
  
  geno_table
}

```

### geno_heatmap_df to heatmap plot
```{r heatmapdf2plot_fx}

heatmapdf2plot <- function(geno_df){
  heatmap_plot <- ggplot(geno_df, aes(x = locus, y = Ind, fill = value)) +
    geom_tile() +
    theme_minimal()+ 
    theme(axis.text.x=element_blank(), 
          axis.ticks.x=element_blank(), 
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank())+
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"), 
          text = element_text(size = 12), 
          legend.key.size = unit(1, 'cm')) +
    ylab(label ="Individual")+
    scale_fill_gradient2(low = "#790E0E", mid = "#63666A", high = "#1C197E",
                         midpoint = 3.0, 
                         guide = "colourbar", 
                         na.value = "white")

  #low = "#9BD75E", mid = "#1DC2A6", high = "#1E36C2"
  heatmap_plot
  
}

```

### geno_heatmap_df to bar function
```{r df2bar_fx}

df2bar <- function(geno_df){
  
  id_bar_plot <- ggplot(geno_df, aes(cluster_text, Ind, fill = cluster)) +
    geom_tile() + 
    theme_minimal()+ 
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),  
          axis.line = element_blank(), 
          legend.text = element_text(size = 12), 
          legend.key.size = unit(1, 'cm')) +
    theme(axis.text.x=element_blank(), 
          axis.ticks.x=element_blank(), 
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank()) +
    xlab(label = ". ") +
    ylab(label = " ") +
    scale_fill_manual(values = opt1_region_palette) + 
    theme(legend.position="left") + 
    theme(axis.text.x=element_blank())
    
  id_bar_plot
}

```

### get ld df
```{r define_get_ld_df_fx}

get_LD_df <- function(LINKAGE_FILENAME){
  r <- read.table(LINKAGE_FILENAME, header = FALSE, stringsAsFactors = FALSE)
  
  colnames(r) <- c("snp1", "snp2", "bp_space", "r2", "D", "Dp", "r2_EM")
  
  r_ord <- r[order(r$snp1, r$snp2),]
  for(i in 3:ncol(r_ord)){r_ord[,i] <- as.numeric(r_ord[,i])}
  for(j in 1:2){r_ord[,j] <- as.character(r_ord[,j])}
  
  r_ord
  
}

```

### plot ld heatmap
```{r define_plot_ld_heatmap_fx}

plot_ld_heatmap <- function(LD_DF, max_r2){
  LDHM <- ggplot(data = LD_DF, aes(snp1, snp2, fill = r2))+
    geom_tile()+
	  scale_fill_gradient2(low = "white", 
	                       high = "#86050A", 
	                       mid = "#E2B8A8",
	                       midpoint = max_r2 / 2,
	                       limit = c(0,max_r2),
	                       space = "Lab", 
	                       name="LD") +
    ggtitle("linkage disequilibrium")+
    theme_minimal()+ 
    theme(axis.text.x=element_blank(),
          axis.ticks.x=element_blank(), 
          axis.text.y=element_blank(),  
	  		  axis.ticks.y=element_blank())+
  			  coord_fixed()+
   			  theme(panel.grid.major = element_blank(),
   			        panel.grid.minor = element_blank(),
   			        panel.background = element_blank(), 
   			        axis.line = element_line(colour = "black"),
   			        legend.key.size = unit(1, 'cm'))
  
  LDHM
  
}

```

# specify
## get basic info
```{r project_setup}

#places and names
BASEDIR <- "/home/laura/Liftsphere/CPAL-CPAL260/structural_variants/" #the directory where the metadata file lives
FIG_DIR <- paste0(BASEDIR, "FIGURES/")
PREFIX <- "CPAL-CPAL260-sv" #the prefix for the lcWGS run
#EBS spawning beagles
CHR7_BIT1_BEAGLE_FILENAME <- paste0(BASEDIR, "beagles/", PREFIX, "_chr7-1.beagle")
CHR12_BIT1_BEAGLE_FILENAME <- paste0(BASEDIR, "beagles/", PREFIX, "_chr12-1.beagle")
CHR7_BIT2_BEAGLE_FILENAME <- paste0(BASEDIR, "beagles/", PREFIX, "_chr7-2.beagle")
CHR12_BIT2_BEAGLE_FILENAME <- paste0(BASEDIR, "beagles/", PREFIX, "_chr12-2.beagle")

#ALL-noJP spawning beagles (GOA + UN + EBS + KOTZ)
CHR7_SV_ALL_noJP_BEAGLE_FILENAME <- paste0(BASEDIR, "beagles/", PREFIX, "_ALL-noJP_chr7-2.beagle")
CHR12_SV_ALL_noJP_BEAGLE_FILENAME <- paste0(BASEDIR, "beagles/", PREFIX, "_ALL-noJP_chr12-2.beagle")

#ALL spawning beagles (JP + GOA + UN + EBS + KOTZ)
CHR7_SV_ALL_BEAGLE_FILENAME <- paste0(BASEDIR, "beagles/", PREFIX, "_ALL_chr7-2.beagle")
CHR12_SV_ALL_BEAGLE_FILENAME <- paste0(BASEDIR, "beagles/", PREFIX, "_ALL_chr12-2.beagle")

#chromosomes
CHROMFILE <- "/home/laura/Liftsphere/CPAL-CPAL260/Clupal_chrom_metadata.txt"
chrom_df <- read.table(CHROMFILE, header = TRUE)

#metadata
METADATAFILE <- "/home/laura/Liftsphere/CPAL-CPAL260/pacific-herring-260_metadata.xlsx" #metadatafile name (excel file)
SHEET <- "Sheet1" #sheet containing the pertinent metadata
metadata <- read_xlsx(METADATAFILE, sheet = SHEET)
ebs_metadata_df <- metadata %>%
  filter(final_eBSAI == 1) %>%
  filter(spawning == "spawning")
sv_metadata_df <- metadata %>%
  filter(sv_dataset == 1)

#palette
opt1_region_palette <- c("Constantine Bay" = "#d9d2e9",
                         "Port Moller" = "#cbacc9",
                         "Togiak" = "#bc86a9",
                         "Goodnews Bay" = "#ae6089",
                         "Kangirlvar Bay" = "#964779",
                         "Nelson Island" = "#763878",
                         "Norton Sound" = "#562a77",
                         "Kotzebue" = "#351c75",
                         "Popof Island" = "#fdd0a2",
                         "Kodiak - Kiliuda" = "#fd8d3c",
                         "Kodiak - Uganik" = "#d94801",
                         "Cordova" = "#8c2d04",
                         "Unalaska" = "#808080",
                         "Japan" = "#000000",
                         "A" = "#07520D",
                         "B" = "#47824C",
                         "C" = "#88B48C",
                         "D" = "#C7E5CA")

#theme
theme_set(
  theme( 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 90, size = 10, vjust = 0.5),
    axis.text.y = element_text(angle = 0, size = 10),
    panel.background = element_rect(fill = "white"), 
    panel.spacing = unit(0,"lines"),
    strip.text.y = element_text(angle = 0) 
  )
)

#scales::show_col(opt1_region_palette, labels = FALSE)

```


# FST: CPAL-CPAL260-sv clusters 
## Manhattan plots
```{r ebs_spawning_clust_fst_manh}

window_size_bp <- 95000
window_avg_threshold <- 10
subset_n <- 100

clusts <- c("A", "B", "C", "D")
for (clust in clusts) {
  clust_df <- FST_df_prep(chrom_df, clusts, clust, window_size_bp, window_avg_threshold, subset_n)
  clust_manh_plot <- ggplot(data = clust_df, aes(x = midpos, y = fst_neg0)) +
    geom_point(aes(color=as.factor(chr_num)), alpha = 0.5) +
    geom_path(aes(x = midpos, y = window_fst), color = "darkblue") +
    scale_color_manual(values = rep(c("lightblue", "lightgrey"), 25 )) +
    facet_grid(POP2 ~ chr_num, scales = "free_x") +
    scale_y_continuous(breaks=c(0.0, 0.25, 0.5, 0.75, 1), limits=c(0, 1)) +
    scale_x_continuous(breaks = c(1e7,2e7)) +
    ylab(expression(italic(F[ST]))) +
    xlab("Chromosome position (Mb)") +
    ggtitle(paste0(PREFIX, ": cluster ", clust, " vs all"))
  
  # ggsave(paste0(FIG_DIR, 
  #               PREFIX, 
  #               "_cluster", 
  #               clust, 
  #               "_subset",
  #               subset_n,
  #               "_",
  #               window_size_bp, 
  #               "-", 
  #               window_avg_threshold,
  #               ".fst.jpg"), 
  #        width = 10, 
  #        height = 8, 
  #        units = "in",
  #        dpi = 600)
}

```



## localize sv margins
### A vs C
#### A-C FST df setup
```{r AC_fst_setup}

window_size_bp <- 100000
window_avg_threshold <- 100000
subset_n <- 0

AC_clusts <- c("A", "C")
A_clust <- "A"
clustA_df <- FST_df_prep(chrom_df, AC_clusts, A_clust, window_size_bp, window_avg_threshold, subset_n)
chr7_AC_df <- clustA_df %>%
  filter(chr_num == 7)
chr12_AC_df <- clustA_df %>%
  filter(chr_num == 12)
rm(clustA_df)

```

#### A-C FST chr7
```{r AC_chr7_manh}

chr7_AC_0.5fst_sv_df <- chr7_AC_df %>%
  filter(fst_neg0 >= 0.5) %>%
  filter(midpos >= 2.0e7 & midpos <= 2.8e7)
chr7_AC_sv_start_pos <- min(chr7_AC_0.5fst_sv_df$midpos, na.rm = T)
chr7_AC_sv_end_pos <- max(chr7_AC_0.5fst_sv_df$midpos, na.rm = T)

(chr7_AC_manh <- ggplot(data = chr7_AC_df, aes(x = midpos, y = fst_neg0)) +
    geom_point(aes(color=as.factor(chr_num)), alpha = 0.5) +
    geom_vline(aes(xintercept = chr7_AC_sv_start_pos), color = "black") +
    geom_vline(aes(xintercept = chr7_AC_sv_end_pos), color = "black") +
    scale_color_manual(values = rep(c("lightblue", "lightgrey"), 25 )) +
    xlim(c(2.0e7,2.8e7)) +
    ylab(expression(italic(F[ST]))) +
    xlab("Chromosome position (Mb)") +
    ggtitle("CPAL-CPAL260-sv: cluster A vs cluster C, chr7 only"))

```



#### A-C FST chr12
```{r AC_chr12_manh}

chr12_AC_0.5fst_sv_df <- chr12_AC_df %>%
  filter(fst_neg0 >= 0.5) %>%
  filter(midpos >= 1.75e7 & midpos <= 2.75e7)
chr12_AC_sv_start_pos <- min(chr12_AC_0.5fst_sv_df$midpos, na.rm = T)
chr12_AC_sv_end_pos <- max(chr12_AC_0.5fst_sv_df$midpos, na.rm = T)

(chr12_AC_manh <- ggplot(data = chr12_AC_df, aes(x = midpos, y = fst_neg0)) +
    geom_point(aes(color=as.factor(chr_num)), alpha = 0.5) +
    geom_vline(aes(xintercept = chr12_AC_sv_start_pos), color = "black") +
    geom_vline(aes(xintercept = chr12_AC_sv_end_pos), color = "black") +
    scale_color_manual(values = rep(c("lightblue", "lightgrey"), 25 )) +
    xlim(c(1.75e7,2.75e7)) +
    ylab(expression(italic(F[ST]))) +
    xlab("Chromosome position (Mb)") +
    ggtitle("CPAL-CPAL260-sv: cluster A vs cluster C, chr12 only"))

```



### B vs D
#### B-D FST df setup
```{r BD_fst_setup}

window_size_bp <- 100000
window_avg_threshold <- 100000
subset_n <- 0

BD_clusts <- c("B", "D")
B_clust <- "B"
clustB_df <- FST_df_prep(chrom_df, BD_clusts, B_clust, window_size_bp, window_avg_threshold, subset_n)
chr7_BD_df <- clustB_df %>%
  filter(chr_num == 7)
chr12_BD_df <- clustB_df %>%
  filter(chr_num == 12)
rm(clustB_df)

```

#### B-D FST chr7
```{r BD_chr7_manh}

chr7_BD_0.5fst_sv_df <- chr7_BD_df %>%
  filter(fst_neg0 >= 0.5) %>%
  filter(midpos >= 2.0e7 & midpos <= 2.8e7)
chr7_BD_sv_start_pos <- min(chr7_BD_0.5fst_sv_df$midpos, na.rm = T)
chr7_BD_sv_end_pos <- max(chr7_BD_0.5fst_sv_df$midpos, na.rm = T)

(chr7_BD_manh <- ggplot(data = chr7_BD_df, aes(x = midpos, y = fst_neg0)) +
    geom_point(aes(color=as.factor(chr_num)), alpha = 0.5) +
    geom_vline(aes(xintercept = chr7_BD_sv_start_pos), color = "black") +
    geom_vline(aes(xintercept = chr7_BD_sv_end_pos), color = "black") +
    scale_color_manual(values = rep(c("lightblue", "lightgrey"), 25 )) +
    xlim(c(2.0e7,2.8e7)) +
    ylab(expression(italic(F[ST]))) +
    xlab("Chromosome position (Mb)") +
    ggtitle("CPAL-CPAL260-sv: cluster B vs cluster D, chr7 only"))

```



#### B-D FST chr12
```{r BD_chr12_manh}

chr12_BD_0.5fst_sv_df <- chr12_BD_df %>%
  filter(fst_neg0 >= 0.5) %>%
  filter(midpos >= 1.75e7 & midpos <= 2.75e7)
chr12_BD_sv_start_pos <- min(chr12_BD_0.5fst_sv_df$midpos, na.rm = T)
chr12_BD_sv_end_pos <- max(chr12_BD_0.5fst_sv_df$midpos, na.rm = T)

(chr12_BD_manh <- ggplot(data = chr12_BD_df, aes(x = midpos, y = fst_neg0)) +
   geom_point(aes(color=as.factor(chr_num)), alpha = 0.5) +
   # geom_vline(aes(xintercept = chr12_BD_sv_start_pos), color = "black") +
   geom_vline(aes(xintercept = chr12_BD_sv_end_pos), color = "black") +
   scale_color_manual(values = rep(c("lightblue", "lightgrey"), 25 )) +
   xlim(c(1.75e7,2.75e7)) +
   ylab(expression(italic(F[ST]))) +
   xlab("Chromosome position (Mb)") +
   ggtitle("CPAL-CPAL260-sv: cluster B vs cluster D, chr12 only"))

```



### SV margins summary
```{r print_sv_margins}

sv_manh_plots <- ggarrange(chr7_AC_manh, chr12_AC_manh, chr7_BD_manh, chr12_BD_manh, ncol = 2, nrow = 2, common.legend = TRUE)
#ggsave(paste0(FIG_DIR, PREFIX, "_fst_manh.fst.jpg"), width = 16, height = 10, units = "in", dpi = 600)

print(paste0("chromosome 7, A vs C, start pos: ", chr7_AC_sv_start_pos, "; end pos: ", chr7_AC_sv_end_pos))
print(paste0("chromosome 7, B vs D, start pos: ", chr7_BD_sv_start_pos, "; end pos: ", chr7_BD_sv_end_pos))
print(paste0("chromosome 12, A vs C, start pos: ", chr12_AC_sv_start_pos, "; end pos: ", chr12_AC_sv_end_pos))
print(paste0("chromosome 12, B vs D, start pos: ", chr12_BD_sv_start_pos, "; end pos: ", chr12_BD_sv_end_pos))

```


### What's that weird break in chr7's sv?
```{r chr7_sv_break}

break_start_pos <- 2.6313e7
break_end_pos <- 2.64525e7

chr7_AC_manh <- ggplot(data = chr7_AC_df, aes(x = midpos, y = fst_neg0)) +
    geom_point(aes(color=as.factor(chr_num)), alpha = 0.5) +
    geom_vline(aes(xintercept = break_start_pos), color = "black", linetype = 3) +
    geom_vline(aes(xintercept = break_end_pos), color = "black", linetype = 3) +
    scale_color_manual(values = rep(c("lightblue", "lightgrey"), 25 )) +
    xlim(c(2.625e7,2.65e7)) +
    ylab(expression(italic(F[ST]))) +
    xlab("Chromosome position (Mb)") +
    ggtitle("CPAL-CPAL260-sv: chr7 break, cluster A vs cluster C")

chr7_BD_manh <- ggplot(data = chr7_BD_df, aes(x = midpos, y = fst_neg0)) +
    geom_point(aes(color=as.factor(chr_num)), alpha = 0.5) +
    geom_vline(aes(xintercept = break_start_pos), color = "black", linetype = 3) +
    geom_vline(aes(xintercept = break_end_pos), color = "black", linetype = 3) +
    scale_color_manual(values = rep(c("lightblue", "lightgrey"), 25 )) +
    xlim(c(2.625e7,2.65e7)) +
    ylab(expression(italic(F[ST]))) +
    xlab("Chromosome position (Mb)") +
    ggtitle("CPAL-CPAL260-sv: chr7 break, cluster B vs cluster D")

ggarrange(chr7_AC_manh, chr7_BD_manh, nrow = 2, common.legend = T)

#ggsave(paste0(FIG_DIR, PREFIX, "_chr7-sv-break_fst_manh.fst.jpg"), width = 10, height = 10, units = "in", dpi = 600)

```

## SVs in other populations
### spawning GOA
```{r goa_manh}

window_size_bp <- 10000
window_avg_threshold <- 5
subset_n <- 10

goa_clusts <- c("A", "B", "C", "D", "goa")
goa_clust <- "goa"
goa_fst_df <- FST_df_prep(chrom_df, goa_clusts, goa_clust, window_size_bp, window_avg_threshold, subset_n)

nrow(goa_fst_df)
sum(is.na(goa_fst_df$window_fst) == FALSE)

(goa_manh_plot <- ggplot(data = goa_fst_df, aes(x = midpos, y = fst_neg0)) +
    geom_point(aes(color=as.factor(chr_num)), alpha = 0.5) +
    geom_vline(data = filter(goa_fst_df, chr_num == 7), aes(xintercept = chr7_BD_sv_start_pos), color = "black", linetype = 3) +
    geom_vline(data = filter(goa_fst_df, chr_num == 7), aes(xintercept = chr7_AC_sv_end_pos), color = "black", linetype = 3) +
    geom_vline(data = filter(goa_fst_df, chr_num == 12), aes(xintercept = chr12_AC_sv_start_pos), color = "black", linetype = 3) +
    geom_vline(data = filter(goa_fst_df, chr_num == 12), aes(xintercept = chr12_AC_sv_end_pos), color = "black", linetype = 3) +
    #geom_path(aes(x = midpos, y = window_fst), color = "darkblue") +
    scale_color_manual(values = rep(c("lightblue", "lightgrey"), 25 )) +
    facet_grid(POP2 ~ chr_num, scales = "free_x") +
    scale_y_continuous(breaks=c(0.0, 0.25, 0.5, 0.75, 1), limits=c(0, 1)) +
    scale_x_continuous(breaks = c(1e7,2e7)) +
    ylab(expression(italic(F[ST]))) +
    xlab("Chromosome position (Mb)") +
    ggtitle(paste0(PREFIX, ": cluster ", clust, " vs all")))
  
# ggsave(paste0(FIG_DIR,
#               PREFIX,
#               "_cluster",
#               clust,
#               "_subset",
#               subset_n,
#               "_",
#               window_size_bp,
#               "-",
#               window_avg_threshold,
#               ".fst.jpg"),
#        width = 10,
#        height = 8,
#        units = "in",
#        dpi = 600)

```



### non-spawning GOA
```{r popof_manh}

window_size_bp <- 10000
window_avg_threshold <- 5
subset_n <- 10

popof_clusts <- c("A", "B", "C", "D", "popof")
popof_clust <- "popof"
popof_fst_df <- FST_df_prep(chrom_df, popof_clusts, popof_clust, window_size_bp, window_avg_threshold, subset_n)

nrow(popof_fst_df)
sum(is.na(popof_fst_df$window_fst) == FALSE)

(popof_manh_plot <- ggplot(data = popof_fst_df, aes(x = midpos, y = fst_neg0)) +
    geom_point(aes(color=as.factor(chr_num)), alpha = 0.5) +
    geom_vline(data = filter(goa_fst_df, chr_num == 7), aes(xintercept = chr7_BD_sv_start_pos), color = "black", linetype = 3) +
    geom_vline(data = filter(goa_fst_df, chr_num == 7), aes(xintercept = chr7_AC_sv_end_pos), color = "black", linetype = 3) +
    geom_vline(data = filter(goa_fst_df, chr_num == 12), aes(xintercept = chr12_AC_sv_start_pos), color = "black", linetype = 3) +
    geom_vline(data = filter(goa_fst_df, chr_num == 12), aes(xintercept = chr12_AC_sv_end_pos), color = "black", linetype = 3) +
    #geom_path(aes(x = midpos, y = window_fst), color = "darkblue") +
    scale_color_manual(values = rep(c("lightblue", "lightgrey"), 25 )) +
    facet_grid(POP2 ~ chr_num, scales = "free_x") +
    scale_y_continuous(breaks=c(0.0, 0.25, 0.5, 0.75, 1), limits=c(0, 1)) +
    scale_x_continuous(breaks = c(1e7,2e7)) +
    ylab(expression(italic(F[ST]))) +
    xlab("Chromosome position (Mb)") +
    ggtitle(paste0(PREFIX, ": cluster ", clust, " vs all")))
  
# ggsave(paste0(FIG_DIR,
#               PREFIX,
#               "_cluster",
#               clust,
#               "_subset",
#               subset_n,
#               "_",
#               window_size_bp,
#               "-",
#               window_avg_threshold,
#               ".fst.jpg"),
#        width = 10,
#        height = 8,
#        units = "in",
#        dpi = 600)

```


### kotzebue
```{r kotzebue_manh}

window_size_bp <- 10000
window_avg_threshold <- 5
subset_n <- 10

kotzebue_clusts <- c("A", "B", "C", "D", "kotzebue")
kotzebue_clust <- "kotzebue"
kotzebue_fst_df <- FST_df_prep(chrom_df, kotzebue_clusts, kotzebue_clust, window_size_bp, window_avg_threshold, subset_n)

nrow(kotzebue_fst_df)
sum(is.na(kotzebue_fst_df$window_fst) == FALSE)

(kotzebue_manh_plot <- ggplot(data = kotzebue_fst_df, aes(x = midpos, y = fst_neg0)) +
    geom_point(aes(color=as.factor(chr_num)), alpha = 0.5) +
    geom_vline(data = filter(kotzebue_fst_df, chr_num == 7), aes(xintercept = chr7_BD_sv_start_pos), color = "black", linetype = 3) +
    geom_vline(data = filter(kotzebue_fst_df, chr_num == 7), aes(xintercept = chr7_AC_sv_end_pos), color = "black", linetype = 3) +
    geom_vline(data = filter(kotzebue_fst_df, chr_num == 12), aes(xintercept = chr12_AC_sv_start_pos), color = "black", linetype = 3) +
    geom_vline(data = filter(kotzebue_fst_df, chr_num == 12), aes(xintercept = chr12_AC_sv_end_pos), color = "black", linetype = 3) +
    #geom_path(aes(x = midpos, y = window_fst), color = "darkblue") +
    scale_color_manual(values = rep(c("lightblue", "lightgrey"), 25 )) +
    facet_grid(POP2 ~ chr_num, scales = "free_x") +
    scale_y_continuous(breaks=c(0.0, 0.25, 0.5, 0.75, 1), limits=c(0, 1)) +
    scale_x_continuous(breaks = c(1e7,2e7)) +
    ylab(expression(italic(F[ST]))) +
    xlab("Chromosome position (Mb)") +
    ggtitle(paste0(PREFIX, ": cluster ", kotzebue_clust, " vs all")))
  
# ggsave(paste0(FIG_DIR,
#               PREFIX,
#               "_cluster",
#               kotzebue_clust,
#               "_subset",
#               subset_n,
#               "_",
#               window_size_bp,
#               "-",
#               window_avg_threshold,
#               ".fst.jpg"),
#        width = 10,
#        height = 8,
#        units = "in",
#        dpi = 600)

```



### unalaska
```{r unalaska_manh}

window_size_bp <- 10000
window_avg_threshold <- 5
subset_n <- 10

unalaska_clusts <- c("A", "B", "C", "D", "unalaska")
unalaska_clust <- "unalaska"
unalaska_fst_df <- FST_df_prep(chrom_df, unalaska_clusts, unalaska_clust, window_size_bp, window_avg_threshold, subset_n)

nrow(unalaska_fst_df)
sum(is.na(unalaska_fst_df$window_fst) == FALSE)

(unalaska_manh_plot <- ggplot(data = unalaska_fst_df, aes(x = midpos, y = fst_neg0)) +
    geom_point(aes(color=as.factor(chr_num)), alpha = 0.5) +
    geom_vline(data = filter(unalaska_fst_df, chr_num == 7), aes(xintercept = chr7_BD_sv_start_pos), color = "black", linetype = 3) +
    geom_vline(data = filter(unalaska_fst_df, chr_num == 7), aes(xintercept = chr7_AC_sv_end_pos), color = "black", linetype = 3) +
    geom_vline(data = filter(unalaska_fst_df, chr_num == 12), aes(xintercept = chr12_AC_sv_start_pos), color = "black", linetype = 3) +
    geom_vline(data = filter(unalaska_fst_df, chr_num == 12), aes(xintercept = chr12_AC_sv_end_pos), color = "black", linetype = 3) +
    #geom_path(aes(x = midpos, y = window_fst), color = "darkblue") +
    scale_color_manual(values = rep(c("lightblue", "lightgrey"), 25 )) +
    facet_grid(POP2 ~ chr_num, scales = "free_x") +
    scale_y_continuous(breaks=c(0.0, 0.25, 0.5, 0.75, 1), limits=c(0, 1)) +
    scale_x_continuous(breaks = c(1e7,2e7)) +
    ylab(expression(italic(F[ST]))) +
    xlab("Chromosome position (Mb)") +
    ggtitle(paste0(PREFIX, ": cluster ", unalaska_clust, " vs all")))
  
# ggsave(paste0(FIG_DIR,
#               PREFIX,
#               "_cluster",
#               unalaska_clust,
#               "_subset",
#               subset_n,
#               "_",
#               window_size_bp,
#               "-",
#               window_avg_threshold,
#               ".fst.jpg"),
#        width = 10,
#        height = 8,
#        units = "in",
#        dpi = 600)

```



# PCAs
## chr 7
### chr7 - bit 1
```{r pca_chr7_bit1}

covfile_chr7_bit1 <- as.matrix(read.table(paste0(BASEDIR, "pca/", PREFIX, "_chr7-1.cov")))
features_df <- sv_metadata_df[c("Barcode", "MarineRegion", "eBSAI_clust_CORRECTED")]
colnames(features_df) <- c("Barcode", "color_feature", "shape_feature")

(pca_chr7_bit1 <- plot_pca(features_df, covfile_chr7_bit1))

#ggsave(paste0(FIG_DIR, PREFIX, "_chr7-1_PCA.jpg"), width = 8, height = 6, units = "in", dpi = 600)

```


### chr7 - bit 2
```{r pca_chr7_bit2}

covfile_chr7_bit2 <- as.matrix(read.table(paste0(BASEDIR, "pca/", PREFIX, "_chr7-2.cov")))
features_df <- sv_metadata_df[c("Barcode", "MarineRegion", "eBSAI_clust_CORRECTED")]
colnames(features_df) <- c("Barcode", "color_feature", "shape_feature")

(pca_chr7_bit2 <- plot_pca(features_df, covfile_chr7_bit2))

#ggsave(paste0(FIG_DIR, PREFIX, "_chr7-2_PCA.jpg"), width = 8, height = 6, units = "in", dpi = 600)

```


## chr12
### chr12 - bit 1
```{r pca_chr12_bit1}

covfile_chr12_bit1 <- as.matrix(read.table(paste0(BASEDIR, "pca/", PREFIX, "_chr12-1.cov")))
features_df <- sv_metadata_df[c("Barcode", "MarineRegion", "eBSAI_clust_CORRECTED")]
colnames(features_df) <- c("Barcode", "color_feature", "shape_feature")

(pca_chr12_bit1 <- plot_pca(features_df, covfile_chr12_bit1))

#ggsave(paste0(FIG_DIR, PREFIX, "_chr12-1_PCA.jpg"), width = 8, height = 6, units = "in", dpi = 600)

```


### chr12 - bit 2
```{r pca_chr12_bit2}

covfile_chr12_bit2 <- as.matrix(read.table(paste0(BASEDIR, "pca/", PREFIX, "_chr12-2.cov")))
features_df <- sv_metadata_df[c("Barcode", "MarineRegion", "eBSAI_clust_CORRECTED")]
colnames(features_df) <- c("Barcode", "color_feature", "shape_feature")

(pca_chr12_bit2 <- plot_pca(features_df, covfile_chr12_bit2))

#ggsave(paste0(FIG_DIR, PREFIX, "_chr12-2_PCA.jpg"), width = 8, height = 6, units = "in", dpi = 600)

```

# Linkage heatmaps
## chr7
### chr7 - bit 2 (structural variant), by genotype (A+D vs B+C)
```{r chr7_bit2_geno_ld_heatmap}

chr7_bit2_geno1_ld_filename <- paste0(BASEDIR, "ld/", 
                                      PREFIX, "_AD_chr7-2_250snps.ld")
chr7_bit2_geno2_ld_filename <- paste0(BASEDIR, "ld/", 
                                      PREFIX, "_BC_chr7-2_250snps.ld")
  
chr7_bit2_geno1_ld_df <- get_LD_df(chr7_bit2_geno1_ld_filename)
chr7_bit2_geno2_ld_df <- get_LD_df(chr7_bit2_geno2_ld_filename)
chr7_bit2_ld_maxR2 <- max(c(chr7_bit2_geno1_ld_df$r2, chr7_bit2_geno2_ld_df$r2), na.rm = TRUE)
chr7_bit2_geno1_ld_heatmap <- plot_ld_heatmap(chr7_bit2_geno1_ld_df, chr7_bit2_ld_maxR2)
chr7_bit2_geno2_ld_heatmap <- plot_ld_heatmap(chr7_bit2_geno2_ld_df, chr7_bit2_ld_maxR2)
(chr7_bit2_genos_ld_heatmap <- ggarrange(chr7_bit2_geno1_ld_heatmap,
                                         chr7_bit2_geno2_ld_heatmap,
                                         ncol = 2,
                                         nrow = 1,
                                         common.legend = T))
# ggsave(paste0(FIG_DIR, PREFIX, "_chr7-2_250snps_by-genotype_linkage-heatmap.jpeg"),
#        width = 12, height = 6,
#        dpi = 600, units = "in")

```



## chr12
### chr12 - bit 2 (structural variant), by genotype (A+B vs C+D)
```{r chr12_bit2_geno_ld_heatmap}

chr12_bit2_geno1_ld_filename <- paste0(BASEDIR, "ld/", 
                                      PREFIX, "_CD_chr12-2_250snps.ld")
chr12_bit2_geno2_ld_filename <- paste0(BASEDIR, "ld/", 
                                      PREFIX, "_AB_chr12-2_250snps.ld")
  
chr12_bit2_geno1_ld_df <- get_LD_df(chr12_bit2_geno1_ld_filename)
chr12_bit2_geno2_ld_df <- get_LD_df(chr12_bit2_geno2_ld_filename)
chr12_bit2_ld_maxR2 <- max(c(chr12_bit2_geno1_ld_df$r2, chr12_bit2_geno2_ld_df$r2), na.rm = TRUE)
chr12_bit2_geno1_ld_heatmap <- plot_ld_heatmap(chr12_bit2_geno1_ld_df, chr12_bit2_ld_maxR2)
chr12_bit2_geno2_ld_heatmap <- plot_ld_heatmap(chr12_bit2_geno2_ld_df, chr12_bit2_ld_maxR2)
(chr12_bit2_genos_ld_heatmap <- ggarrange(chr12_bit2_geno1_ld_heatmap,
                                          chr12_bit2_geno2_ld_heatmap,
                                          ncol = 2,
                                          nrow = 1,
                                          common.legend = T))
# ggsave(paste0(FIG_DIR, PREFIX, "_chr12-2_250snps_by-genotype_linkage-heatmap.jpeg"),
#        width = 12, height = 6,
#        dpi = 600, units = "in")

```



# Genotype heatmaps
## heatmap setup
```{r heatmap_setup}

features_df <- sv_metadata_df[c("Barcode", "MarineRegion", "eBSAI_clust_CORRECTED")]

ind_list <- c()
for (ind_num in 1:nrow(features_df)) {
  ind_list <- append(ind_list, paste0("Ind", ind_num))
}

features_df$Ind <- ind_list

```

## chr7
### chr7 - bit 1
```{r chr7_bit1_genoheatmap}

chr7_bit1_heatmap_table <- beagle2heatmapdf(CHR7_BIT1_BEAGLE_FILENAME)
chr7_bit1_geno_plot_df <- left_join(chr7_bit1_heatmap_table, features_df)

## Factor the feature into the order you want them to plot
chr7_bit1_geno_plot_df$cluster <- factor(chr7_bit1_geno_plot_df$eBSAI_clust_CORRECTED, levels = c("A", "B", "C", "D"))
chr7_bit1_geno_plot_df$Ind <- factor(chr7_bit1_geno_plot_df$Ind, 
                            levels = unique((chr7_bit1_geno_plot_df$Ind)[order(chr7_bit1_geno_plot_df$cluster)]))

# Plot your genotype heatmap 
chr7_bit1_geno_heatmap <- heatmapdf2plot(chr7_bit1_geno_plot_df)

## Make the colored bar that is for your population colors 
## this will serve as your X-axis and your population ID will serve as your y-axis
chr7_bit1_geno_plot_df <- chr7_bit1_geno_plot_df %>% 
  mutate(cluster_text = "cluster")

# plot a bar that represents population ids for the individuals in rows of the genotype heatmap
chr7_bit1_geno_bar <- df2bar(chr7_bit1_geno_plot_df)

(chr7_bit1_full_geno_heatmap <- ggarrange(chr7_bit1_geno_bar, chr7_bit1_geno_heatmap, widths = c(0.3, 1)))

ggsave(paste0(FIG_DIR, PREFIX, "_chr7-1_genotype-heatmap.jpg"), width = 12, height = 8, units = "in", dpi = 600)

```



### chr7 - bit 2
#### EBS spawning pops
```{r chr7_bit2_EBS_genoheatmap}

chr7_bit2_heatmap_table <- beagle2heatmapdf(CHR7_BIT2_BEAGLE_FILENAME)
chr7_bit2_geno_plot_df <- left_join(chr7_bit2_heatmap_table, features_df)

## Factor the feature into the order you want them to plot
chr7_bit2_geno_plot_df$cluster <- factor(chr7_bit2_geno_plot_df$eBSAI_clust_CORRECTED, levels = c("A", "B", "C", "D"))
chr7_bit2_geno_plot_df$Ind <- factor(chr7_bit2_geno_plot_df$Ind, 
                            levels = unique((chr7_bit2_geno_plot_df$Ind)[order(chr7_bit2_geno_plot_df$cluster)]))

# Plot your genotype heatmap 
chr7_bit2_geno_heatmap <- heatmapdf2plot(chr7_bit2_geno_plot_df)

## Make the colored bar that is for your population colors 
## this will serve as your X-axis and your population ID will serve as your y-axis
chr7_bit2_geno_plot_df <- chr7_bit2_geno_plot_df %>% 
  mutate(cluster_text = "cluster")

# plot a bar that represents population ids for the individuals in rows of the genotype heatmap
chr7_bit2_geno_bar <- df2bar(chr7_bit2_geno_plot_df)

(chr7_bit2_full_geno_heatmap <- ggarrange(chr7_bit2_geno_bar, chr7_bit2_geno_heatmap, widths = c(0.3, 1)))

#ggsave(paste0(FIG_DIR, PREFIX, "_chr7-2_genotype-heatmap.jpg"), width = 12, height = 8, units = "in", dpi = 600)

```



#### GOA + UN + EBS + KOTZ (ALL-noJP)
```{r chr7_sv_ALL-noJP_genoheatmap}

chr7_sv_all_nojp_heatmap_table <- beagle2heatmapdf(CHR7_SV_ALL_noJP_BEAGLE_FILENAME)
chr7_sv_all_nojp_geno_plot_df <- left_join(chr7_sv_all_nojp_heatmap_table, features_df)

## Factor the feature into the order you want them to plot
chr7_sv_all_nojp_geno_plot_df$cluster <- factor(chr7_sv_all_nojp_geno_plot_df$cluster, levels = c("A", "B", "C", "D", "Unalaska", "Kotzebue", "GOA"))
chr7_sv_all_nojp_geno_plot_df$Ind <- factor(chr7_sv_all_nojp_geno_plot_df$Ind, 
                            levels = unique((chr7_sv_all_nojp_geno_plot_df$Ind)[order(chr7_sv_all_nojp_geno_plot_df$cluster)]))

# Plot your genotype heatmap 
chr7_sv_all_nojp_geno_heatmap <- heatmapdf2plot(chr7_sv_all_nojp_geno_plot_df)

## Make the colored bar that is for your population colors 
## this will serve as your X-axis and your population ID will serve as your y-axis
chr7_sv_all_nojp_geno_plot_df <- chr7_sv_all_nojp_geno_plot_df %>% 
  mutate(cluster_text = "cluster")

# plot a bar that represents population ids for the individuals in rows of the genotype heatmap
chr7_sv_all_nojp_geno_bar <- df2bar(chr7_sv_all_nojp_geno_plot_df)

(chr7_sv_all_nojp_full_geno_heatmap <- ggarrange(chr7_sv_all_nojp_geno_bar, chr7_sv_all_nojp_geno_heatmap, widths = c(0.3, 1)))

ggsave(paste0(FIG_DIR, PREFIX, "_ALL-noJP_chr7-2_genotype-heatmap.jpg"), width = 12, height = 8, units = "in", dpi = 600)

```



#### JP + GOA + UN + EBS + KOTZ (ALL)
```{r chr7_sv_ALL_genoheatmap}

chr7_sv_all_heatmap_table <- beagle2heatmapdf(CHR7_SV_ALL_BEAGLE_FILENAME)
chr7_sv_all_geno_plot_df <- left_join(chr7_sv_all_heatmap_table, features_df)

## Factor the feature into the order you want them to plot
chr7_sv_all_geno_plot_df$cluster <- factor(chr7_sv_all_geno_plot_df$cluster, levels = c("A", "B", "C", "D", "Unalaska", "Kotzebue", "GOA", "Japan"))
chr7_sv_all_geno_plot_df$Ind <- factor(chr7_sv_all_geno_plot_df$Ind, 
                            levels = unique((chr7_sv_all_geno_plot_df$Ind)[order(chr7_sv_all_geno_plot_df$cluster)]))

# Plot your genotype heatmap 
chr7_sv_all_geno_heatmap <- heatmapdf2plot(chr7_sv_all_geno_plot_df)

## Make the colored bar that is for your population colors 
## this will serve as your X-axis and your population ID will serve as your y-axis
chr7_sv_all_geno_plot_df <- chr7_sv_all_geno_plot_df %>% 
  mutate(cluster_text = "cluster")

# plot a bar that represents population ids for the individuals in rows of the genotype heatmap
chr7_sv_all_geno_bar <- df2bar(chr7_sv_all_geno_plot_df)

(chr7_sv_all_full_geno_heatmap <- ggarrange(chr7_sv_all_geno_bar, chr7_sv_all_geno_heatmap, widths = c(0.3, 1)))

ggsave(paste0(FIG_DIR, PREFIX, "_ALL_chr7-2_genotype-heatmap.jpg"), width = 12, height = 8, units = "in", dpi = 600)

```



## chr12
### chr12 - bit 1
```{r chr12_bit1_genoheatmap}

chr12_bit1_heatmap_table <- beagle2heatmapdf(CHR12_BIT1_BEAGLE_FILENAME)
chr12_bit1_geno_plot_df <- left_join(chr12_bit1_heatmap_table, features_df)

## Factor the feature into the order you want them to plot
chr12_bit1_geno_plot_df$cluster <- factor(chr12_bit1_geno_plot_df$eBSAI_clust_CORRECTED, levels = c("A", "B", "C", "D"))
chr12_bit1_geno_plot_df$Ind <- factor(chr12_bit1_geno_plot_df$Ind, 
                            levels = unique((chr12_bit1_geno_plot_df$Ind)[order(chr12_bit1_geno_plot_df$cluster)]))

# Plot your genotype heatmap 
chr12_bit1_geno_heatmap <- heatmapdf2plot(chr12_bit1_geno_plot_df)

## Make the colored bar that is for your population colors 
## this will serve as your X-axis and your population ID will serve as your y-axis
chr12_bit1_geno_plot_df <- chr12_bit1_geno_plot_df %>% 
  mutate(cluster_text = "cluster")

# plot a bar that represents population ids for the individuals in rows of the genotype heatmap
chr12_bit1_geno_bar <- df2bar(chr12_bit1_geno_plot_df)

(chr12_bit1_full_geno_heatmap <- ggarrange(chr12_bit1_geno_bar, chr12_bit1_geno_heatmap, widths = c(0.3, 1)))

#ggsave(paste0(FIG_DIR, PREFIX, "_chr12-1_genotype-heatmap.jpg"), width = 12, height = 8, units = "in", dpi = 600)

```



### chr12 - bit 2
#### EBS spawning pops
```{r chr12_bit2_genoheatmap}

chr12_bit2_heatmap_table <- beagle2heatmapdf(CHR12_BIT2_BEAGLE_FILENAME)
chr12_bit2_geno_plot_df <- left_join(chr12_bit2_heatmap_table, features_df)

## Factor the feature into the order you want them to plot
chr12_bit2_geno_plot_df$cluster <- factor(chr12_bit2_geno_plot_df$eBSAI_clust_CORRECTED, levels = c("A", "B", "C", "D"))
chr12_bit2_geno_plot_df$Ind <- factor(chr12_bit2_geno_plot_df$Ind, 
                            levels = unique((chr12_bit2_geno_plot_df$Ind)[order(chr12_bit2_geno_plot_df$cluster)]))

# Plot your genotype heatmap 
chr12_bit2_geno_heatmap <- heatmapdf2plot(chr12_bit2_geno_plot_df)

## Make the colored bar that is for your population colors 
## this will serve as your X-axis and your population ID will serve as your y-axis
chr12_bit2_geno_plot_df <- chr12_bit2_geno_plot_df %>% 
  mutate(cluster_text = "cluster")

# plot a bar that represents population ids for the individuals in rows of the genotype heatmap
chr12_bit2_geno_bar <- df2bar(chr12_bit2_geno_plot_df)

(chr12_bit2_full_geno_heatmap <- ggarrange(chr12_bit2_geno_bar, chr12_bit2_geno_heatmap, widths = c(0.3, 1)))

#ggsave(paste0(FIG_DIR, PREFIX, "_chr12-2_genotype-heatmap.jpg"), width = 12, height = 8, units = "in", dpi = 600)

```



#### GOA + UN + EBS + KOTZ (ALL-noJP)
```{r chr12_sv_ALL-noJP_genoheatmap}

chr12_sv_all_nojp_heatmap_table <- beagle2heatmapdf(CHR12_SV_ALL_noJP_BEAGLE_FILENAME)
chr12_sv_all_nojp_geno_plot_df <- left_join(chr12_sv_all_nojp_heatmap_table, features_df)

## Factor the feature into the order you want them to plot
chr12_sv_all_nojp_geno_plot_df$cluster <- factor(chr12_sv_all_nojp_geno_plot_df$cluster, levels = c("A", "B", "C", "D", "Unalaska", "Kotzebue", "GOA"))
chr12_sv_all_nojp_geno_plot_df$Ind <- factor(chr12_sv_all_nojp_geno_plot_df$Ind, 
                            levels = unique((chr12_sv_all_nojp_geno_plot_df$Ind)[order(chr12_sv_all_nojp_geno_plot_df$cluster)]))

# Plot your genotype heatmap 
chr12_sv_all_nojp_geno_heatmap <- heatmapdf2plot(chr12_sv_all_nojp_geno_plot_df)

## Make the colored bar that is for your population colors 
## this will serve as your X-axis and your population ID will serve as your y-axis
chr12_sv_all_nojp_geno_plot_df <- chr12_sv_all_nojp_geno_plot_df %>% 
  mutate(cluster_text = "cluster")

# plot a bar that represents population ids for the individuals in rows of the genotype heatmap
chr12_sv_all_nojp_geno_bar <- df2bar(chr12_sv_all_nojp_geno_plot_df)

(chr12_sv_all_nojp_full_geno_heatmap <- ggarrange(chr12_sv_all_nojp_geno_bar, chr12_sv_all_nojp_geno_heatmap, widths = c(0.3, 1)))

ggsave(paste0(FIG_DIR, PREFIX, "_ALL-noJP_chr12-2_genotype-heatmap.jpg"), width = 12, height = 8, units = "in", dpi = 600)

```



#### JP + GOA + UN + EBS + KOTZ (ALL)
```{r chr7_sv_ALL_genoheatmap}

chr12_sv_all_heatmap_table <- beagle2heatmapdf(CHR12_SV_ALL_BEAGLE_FILENAME)
chr12_sv_all_geno_plot_df <- left_join(chr12_sv_all_heatmap_table, features_df)

## Factor the feature into the order you want them to plot
chr12_sv_all_geno_plot_df$cluster <- factor(chr12_sv_all_geno_plot_df$cluster, levels = c("A", "B", "C", "D", "Unalaska", "Kotzebue", "GOA", "Japan"))
chr12_sv_all_geno_plot_df$Ind <- factor(chr12_sv_all_geno_plot_df$Ind, 
                            levels = unique((chr12_sv_all_geno_plot_df$Ind)[order(chr12_sv_all_geno_plot_df$cluster)]))

# Plot your genotype heatmap 
chr12_sv_all_geno_heatmap <- heatmapdf2plot(chr12_sv_all_geno_plot_df)

## Make the colored bar that is for your population colors 
## this will serve as your X-axis and your population ID will serve as your y-axis
chr12_sv_all_geno_plot_df <- chr12_sv_all_geno_plot_df %>% 
  mutate(cluster_text = "cluster")

# plot a bar that represents population ids for the individuals in rows of the genotype heatmap
chr12_sv_all_geno_bar <- df2bar(chr12_sv_all_geno_plot_df)

(chr12_sv_all_full_geno_heatmap <- ggarrange(chr12_sv_all_geno_bar, chr12_sv_all_geno_heatmap, widths = c(0.3, 1)))

ggsave(paste0(FIG_DIR, PREFIX, "_ALL_chr12-2_genotype-heatmap.jpg"), width = 12, height = 8, units = "in", dpi = 600)

```


